For this tutorial, you will be asked to load and visualize data from a zombie outbreak dataset! Your responses will timed, you can stop the assessment at any time. As a reminder, you can press the green arrow in RStudio to run the code and see the resulting data visualization.

**PLEASE BE SURE THAT YOU HAVE COMPLETED THE TUTORIAL BEFORE CONTINUING WITH THE ZOMBIE OUTBREAK DATA**

We'll load minCombinR and several additional libraries to visualize these data:

```{r setup}
library(dplyr)
library(mincombinr)
```

## Loading data

Load the following datasets into your R environment:

* : a table data file
* : a tree data file
* : an image data file

```{r participantAns1}

#ENTER YOUR CODE HERE

```


Plot the tree and image data individually using the specify_single command:

```{r participantAns2}

#ENTER YOUR CODE HERE

```

Create a scatter chart using the 'ID' and 'source' varaibles in the dataset. Call this scatter chart 'exposure_source'

```{r participantAns3}

#ENTER YOUR CODE HERE

```

Create a timeline using the 'ID','dateOfExposureStart', and 'dateOfExposureEnd' varaibles in the dataset. Call this chart 'exposure_timeline'

```{r participantAns4}

#ENTER YOUR CODE HERE

```

Count the number of people that are sick in each ward (use the status and ward variables) and overlay that data on the image. Call this chart 'ward_cases'.

```{r participantAns5}

#ENTER YOUR CODE HERE

```

Create an unaligned combination of of the using 'exposure_source' and 'ward_cases'. Do you notice anything interesting (the answer may be no). Type your response below the code block

```{r participantAns5}

#ENTER YOUR CODE HERE

```

**TYPE YOUR RESPONSE HERE**

Create a small multiple of the phylogenetic tree using 'exposure source' as the facetting variable. Do you notice anything interesting (the answer may be no). Type your response below the code block.

```{r participantAns5}

#ENTER YOUR CODE HERE

```

**TYPE YOUR RESPONSE HERE**

Create a spatially aligned combination between the phylogenetic tree, 'exposure_source', 'exposure_timeline'

```{r participantAns5}

#ENTER YOUR CODE HERE

```

What happens if you try add the 'ward_cases' image to the combination? Type your response below the code block.

```{r participantAns5}

#ENTER YOUR CODE HERE

```

**TYPE YOUR RESPONSE HERE**

Create a color aligned combination between the 'exposure_source', 'exposure_timeline', 'tree' using the 'exposure_type' variable. Do you notice anything interesting? Type your response below the code block.

```{r participantAns5}

#ENTER YOUR CODE HERE

```

**TYPE YOUR RESPONSE HERE**



