
For this tutorial, we'll use the mtcars dataset. As a reminder, you can press the green arrow in RStudio to run the code and see the resulting data visualization.

We'll load minCombinR and several additional libraries to visualize these data:

```{r setup}
library(dplyr)
library(mincombinr)
```

## minCombinR data input commands

minCombinR works with R data.frame variable types, which you can easily load in from the other R packages, or Rdata objects (like the one saved in this tutorial)

```{r loadData}
# Load in the mtcars dataset - now there is an mtcars environment variable
#mtcars<-load("data/mtcars_custom.RData")

#for testing only removing afterwards:
load("../data/mtcars_custom.RData") 
```

However, sometimes you want to load in a bunch of weird and different data and it's not all neccessarily a data.frame. Do this, minCombinR has a special method called input_data, which you can use to load in different tree data types.

**input_data** takes at two commands:

* *file* : path to file containing your data [REQUIRED]

* *dataType* : type of data, which can be one of tree, table, dna, spatial, image  [REQUIRED]

```{r loadData2}
#for change path after testing
tmp<-input_data(file="../data/mtcars_custom.csv",dataType="table")
```

the variable 'tmp' is a special minCombinR data object, which stores your data table as well as other types of data. It is a special object class in R called an S4 object. minCombinR recongnizes these object types and works with them automatically. If you want to get your data out of this object here is what you need to do:

```{r loadData3,eval=FALSE}
#for change path after testing
View(tmp@data[[1]])
```

### Special Annotations for images
minCombinR has a special command for images, which allows you to annotate some useful data. Here's an example, load the image below and run the "annotate_image" command. You can drag a square area, or double click to add a single point.
```{r imageLoad}
interior_img <- input_data(file = system.file("extdata", "random_interior_map.tiff", 
                                              package = "mincombinr"),
                                              dataType = "image")
```

```{r, eval=FALSE}
interior_img <- annotate_image(interior_img)

# The annotations are automatically there now:
# Save the metadata to load later
metadata <- interior_img@data$metadata
View(metadata)
```

Here's what the result should look like:
```{r}
load(file = system.file("extdata", "img_meta.rds", 
                        package = "mincombinr"))

interior_img@data$metadata<-metadata

# Now specify and plot the interior map
img_chart <- specify_single(chart_type = "image", 
                            data = "interior_img")
plot(img_chart)
```

We can do something interesting with this image too! We can chane up the metadata and create a more interesting visualization:

```{r}
# Let's add some arbitrary case counts to the room
interior_img@data$metadata$counts <- c(100,35)

# Now specify and plot the interior map
img_chart <- specify_single(chart_type = "image", 
                            data = "interior_img", 
                            color = "counts")
plot(img_chart)
```


## minCombinR Visualization Commands

minCombinR has three commands that you need to make a chart and also a set of co-ordinated combinations:

* specify_single : creates a single chart

* specify_combination : allows you to specify a combination of charts. This command supports four types of combinations : small_multiples, spatially_aligned, color_aligned, and unaligned

* plot : make the single chart or combination appear on the screen

Here is an example of all this in action. 

```{r exampleAll, eval=FALSE}
#specify two single charts
my_scatter_chart <- specify_single(chart_type = "scatter", data = "mtcars", x = "hp", y = "mpg")
my_bar_chart <- specify_single(chart_type = "bar", data = "mtcars", x = "carb")

# Specify that you want to faciliate a co-ordinated combination using color
color_combo <- specify_combination(combo_type = "color_aligned", 
                                   base_charts = c("my_scatter_chart", "my_bar_chart"),
                                   link_by = "am")
# Now plot!
plot(color_combo)
```

Ok, now lets go through each of these individually, so you can understand what's going on. To complete this tutorial, you will need to write the code in the empty boxes below.

**Step 1:** Create and plot a single scatter chart using the specify_single and plot commands

**specify_single** takes at least two commands:

* *chart_type* : name of the chart you wish to generate (see the helper function base_chart_types() for all possibilities) [REQUIRED]


* *data* : input data used to generate the chart  [REQUIRED]

* *x,y,etc...* :  additional minimal specification parameters needed to generate the chart (see the helpder function base_chart_specs() for a full list of the parameters for each chart type) [CHART TYPE DEPENDENT]

```{r participantAns1}

#WRITE YOUR CODE IN HERE

```

**Step 2:** Create and plot a single bar chart using the specify_single and plot commands

```{r participantAns2}

#WRITE YOUR CODE IN HERE

```


**Step 3:** Specify a color aligned combination using the specify_combination and plot commands

**specify_combination** take three commands:

* *combo_type* : which can be one of small_multiples, spatially_aligned, colour_aligned, or unaligned [REQUIRED]

* *base_charts* : the names of the charts that you want to combine [REQUIRED]

* *link_by* : for spatially_aligned and colour_aligned charts, the variable you want to link by (i.e. "am" in the prior example) [COMBINATION TYPE DEPENDENT]

```{r participantAns3}

#WRITE YOUR CODE IN HERE

```

Combinations also warn you if it is not possible to combined two types of charts. For example, let's make a pie chart and try combine that with a scatter chart and see what happens:

**Step 4:** Create and plot a single pie chart using the specify_single and plot commands (you pick the variable)

```{r participantAns4}

#WRITE YOUR CODE HERE

str(mtcars) #to see list of variable types

```


**Step 5:** Create and plot a spatially aligned combination of the pie chart and bar chart


```{r participantAns5}

#WRITE YOUR CODE HERE

```

## minCombinR Helper commands

```{r,message=FALSE,warning=FALSE,eval=FALSE}
# To see all of the supported chart types
base_chart_types()

```

```{r}
# To see all of the required and optional parameters for specifications of a chart type, in this example, bar chart
base_chart_specs(chart_type="bar") 

```
