For this study, you will be asked to load and visualize data from a zombie outbreak dataset! Your responses will timed, you can stop the assessment at any time. As a reminder, you can press the green arrow in RStudio to run the code and see the resulting data visualization.

**PLEASE BE SURE THAT YOU HAVE COMPLETED THE TUTORIAL BEFORE CONTINUING WITH THE ZOMBIE OUTBREAK DATA**

We'll load minCombinR and several additional libraries to visualize these data:

```{r setup}
library(dplyr)
library(mincombinr)
```

## Loading data

Load the following datasets into your R environment:

* : a table data file
* : a tree data file
* : an image data file

all of these files are located within the  data folder of this directory

```{r participantAns1}

#ENTER YOUR CODE HERE

```



Make some single charts using the specify_single command. To see the possible attributes of this dataset, use the str() command.

Should you need some help getting started, please don't hesitate to ask the study administrator. 

```{r participantAns2}

#ENTER YOUR CODE HERE

```


Make some chart combinations using the specify_combination command.

Should you need some help getting started, please don't hesitate to ask the study administrator. 

```{r participantAns3}

#ENTER YOUR CODE HERE

```



Write down some observations about the Zombie outbreak. For example, how do you think the outbreak might be spreading?

If you can't think of anything at all, or don't have any observations, please indicate that too.

Please write you answers below in point form:


